02_DESeq_characterization

### 2019-09-04 analysis/03_DESeq2_characterization.Rmd
now with PRL-related genes

## Calculate and plot total DEGs

```{r returntotalDEGs, eval = T, results = 'hide'}
DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGs.male_pituitary <- returntotalDEGs(dds.male_pituitary)
DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r totalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad")

plot_grid(a + theme(legend.position = "none"),
          b + theme(legend.position = "none"),
          c,
          d + theme(legend.position = "none"),
          e + theme(legend.position = "none"),
          f,
          nrow = 2, rel_widths = c(0.3, 0.3, 0.4)) 
```

@@

>>>>

@@

## plot genes in a  PRL WGCNA module

```{r wgcna, eval = T}
plotWGCNAcandidates(dds.female_pituitary, colDataFP, "female pituitary")
plotWGCNAcandidates(dds.male_pituitary,colDataMP, "male pituitary")
